### 2015-03-29 paper/Main.tex
Paper sketching

\documentclass{article}

\usepackage{multicol}

\usepackage[version=3]{mhchem} % Package for chemical equation typesetting
\usepackage{siunitx} % Provides the \SI{}{} and \si{} command for typesetting SI units
\usepackage{graphicx} % Required for the inclusion of images
%\usepackage{natbib} % Required to change bibliography style to APA
%\usepackage{amsmath} % Required for some math elements
%{
%      \newtheorem{assumption}{Assumption}
%      \newtheorem{problem}{Problem}
%}
\usepackage{xcolor}
%\usepackage[usenames,dvipsnames]{color}

\usepackage{ulem}
\usepackage{cancel}

\usepackage{amsthm}
\usepackage{amsmath} % Required for some math elements
{
      \newtheorem{definition}{Definition}
      \newtheorem{assumption}{Assumption}
      \newtheorem{problem}{Problem}
      \newtheorem{lemma}{Lemma}
      \newtheorem{theorem}{Theorem}
      \newtheorem{claim}{Claim}
}
\usepackage{algorithm}
\usepackage{algorithmic}
%\renewcommand{\algorithmicrequire}{ \textbf{Input:}} %Use Input in the format of Algorithm
%\renewcommand{\algorithmicensure}{ \textbf{Output:}} %UseOutput in the format of Algorithm
%\usepackage[linesnumbered,vlined,ruled]{algorithm2e}
\usepackage{graphicx}

\usepackage{cite}
%\usepackage{hyperref}
%\usepackage[numbers,sort&compress]{nat}

\usepackage{xcolor}
%\usepackage[usenames,dvipsnames]{color}
%\usepackage{mathrsfs}
\usepackage{amsfonts,amssymb}

%\usepackage{ulem}
%\usepackage{cancel}

\newcommand{\lyp}[1]{\textcolor{red}{#1}}

%\usepackage{indentfirst}
\setlength\parindent{1em} % Removes all indentation from paragraphs

\usepackage{listings}          % format code

\lstset{ %
language=Haskell,                % choose the language of the code
columns=flexible,
lineskip=-1pt,
basicstyle=\ttfamily\small,       % the size of the fonts that are used for the code
numbers=none,                   % where to put the line-numbers
numberstyle=\ttfamily\tiny,      % the size of the fonts that are used for the line-numbers
stepnumber=1,                   % the step between two line-numbers. If it's 1 each line will be numbered
numbersep=5pt,                  % how far the line-numbers are from the code
backgroundcolor=\color{white},  % choose the background color. You must add \usepackage{color}
showspaces=false,               % show spaces adding particular underscores
showstringspaces=false,         % underline spaces within strings
showtabs=false,                 % show tabs within strings adding particular underscores
morekeywords={var},
%  frame=single,                   % adds a frame around the code
tabsize=2,                  % sets default tabsize to 2 spaces
captionpos=none,                   % sets the caption-position to bottom
breaklines=true,                % sets automatic line breaking
breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
title=\lstname,                 % show the filename of files included with \lstinputlisting; also try caption instead of title
escapeinside={(*}{*)},          % if you want to add a comment within your code
keywordstyle=\ttfamily\bfseries,
% commentstyle=\color{Gray},
% stringstyle=\color{Green}
}

%\usepackage{times} % Uncomment to use the Times New Roman font

%----------------------------------------------------------------------------------------
%	DOCUMENT INFORMATION
%----------------------------------------------------------------------------------------

\title{Embedded Domain-Specific Languages:\\ Composable Interpretations with Dependencies} % Title
%\author{Name¢} % Author name

\begin{document}

\maketitle % Insert the title, author and date

\begin{abstract}

\end{abstract}

\section{Introduction}

\section{Composable Interpretations}
Additional interpretations can be added naturally for deep embedding. For instance, if we also want to obtain the depth of a circuit, we can define the following interpretation easily.

\begin{verbatim}
newtype Depth = Depth {depth :: Int}

depthAlg :: CircuitF Depth -> Depth
depthAlg (Identity w)   = Depth 0
depthAlg (Fan w)        = Depth 1
depthAlg (Above x y)	   = Depth (depth x + depth y)
depthAlg (Beside x y)   = Depth (depth x `max` depth y)
depthAlg (Stretch xs x) = Depth (depth x)
\end{verbatim}

However, with shallow embedding, circuits can only have a single semantic domain. Pairing semantics up can provide two interpretations simultaneously \cite{1}, but it is still clumsy and not modular: existing code needs to be revised every time a new interpretations is added. Moreover, for more than two interpretations, we have to either create combinations for each pair of interpretations, or use tuples which generally lack good language support \cite{1}. To allow defining and composing multiple interpretations modularly, we first use a type class to represent the shallow embedding

\begin{verbatim}
class Circuit circuit where
  identity :: Int -> circuit
  fan      :: Int -> circuit
  above    :: circuit -> circuit -> circuit
  beside   :: circuit -> circuit -> circuit
  stretch  :: [Int] -> circuit -> circuit
\end{verbatim}

Each interpretation corresponds to an instance of the type class for the type of that interpretation. The \textbf{newtype} wrapper is needed to allow multiple interpretations over the same underlying type.  For example, we can define "width" and "depth" interpretations as follows:

\begin{verbatim}
newtype Width     = Width     {width :: Int}
newtype Depth     = Depth     {depth :: Int}

instance Circuit Width where
  identity w   = Width w
  fan w        = Width w
  above x y    = x
  beside x y   = Width (gwidth x + gwidth y)
  stretch xs x = Width (sum xs)

instance Circuit Depth where
  identity w   = Depth 0
  fan w        = Depth 1
  above x y    = Depth (gdepth x + gdepth y)
  beside x y   = Depth (depth x `max` gdepth y)
  stretch xs x = x
\end{verbatim}

To state that the semantic domain type i represents is part of a larger collection of types, we use the following type class

\begin{verbatim}
class i :<: e where
  inter :: e -> i
\end{verbatim}

We further define an instance for circuit composition, which gives a semantic domain of type (i1, i2) for the interpretation

\begin{verbatim}
type Compose i1 i2 = (i1, i2)

instance (Circuit i1, Circuit i2) => Circuit (Compose i1 i2) where
  identity w   = (identity w, identity w) 
  fan w        = (fan w, fan w)
  above x y    = (above (inter x) (inter y), above (inter x) (inter y))
  beside x y   = (beside (inter x) (inter y), beside (inter x) (inter y))
  stretch xs x = (stretch xs (inter x), stretch xs (inter x))
\end{verbatim}

Following is the construction of the Brent-Kung parallel prefix circuit:

\begin{verbatim}
c1 :: Circuit circuit => circuit
c1 = (fan 2 `beside` fan 2) `above`
     stretch [2,2] (fan 2) `above`
     (identity 1 `beside` fan 2 `beside` identity 1)
\end{verbatim}

\textit{gwidth} and \textit{gdepth} are defined to recover individual interpretations:

\begin{verbatim}
gwidth :: (Width :<: e) => e -> Int
gwidth = width . inter

gdepth :: (Depth :<: e) => e -> Int
gdepth = depth . inter
\end{verbatim}

Then we can use the above functions to get  different properties of c1, depending on its type. For example, \textit{gwidth (c1 :: Compose Width Depth)} and \textit{gdepth (c1 :: Compose Width Depth)} will give us its width and depth,  respectively.

\section{Dependent interpretations}
The composable interpretation for shallow embedding in the previous section works well with independent circuits. However, when an interpretation depends on other interpretations, the previous approach becomes clumsy as well. 
For example, whether a circuit is well-formed or not depends on the widths of its parts. A new instance for the type \textit{(Compose WellSized width)} is defined to capture this property.

\begin{verbatim}
newtype WellSized = WellSized {wellSized :: Bool}

instance (Circuit width, Width :<: width) => 
          Circuit (Compose WellSized width) where
  identity w   = (WellSized True, identity w)
  fan w        = (WellSized True, fan w)
  above x y    = (WellSized (gwellSized x && gwellSized y 
                             && (gwidth x == gwidth y)),
                  above (inter x) (inter y))
  beside x y   = (WellSized (gwellSized x && gwellSized y),
                  beside (inter x) (inter y))
  stretch xs x = (WellSized (gwellSized x && length xs == gwidth x),
                  stretch xs (inter x))

gwellSized :: (WellSized :<: e) => e -> Bool
gwellSized = wellSized . inter
\end{verbatim}
However, with this approach, we still need to write out the interpretation for \textit{width} together with that for \textit{WellSized}. Instead of explicitly composing two interpretations together when one depends on the other, we want to rely solely on generic composition defined earlier, regardless of whether the two interpretations are independent or not.

\subsection{Type classes with proxies}
One way is to differentiate between input and output semantic domains. By expressing that the type of output domain is part of the type of input domain, we no longer need to output a pair of interpretations for the dependent case. Let's start with a multi-parameter type class for circuit construction.

\begin{verbatim}
class Circuit inn out where
  identity :: Proxy inn -> Int -> out
  fan      :: Proxy inn -> Int -> out
  above    :: inn       -> inn -> out
  beside   :: inn       -> inn -> out
  stretch  :: [Int]     -> inn -> out

data Proxy a = Proxy
\end{verbatim}

The interpretation for \textit{WellSized} can thus be defined in a nicer way:

\begin{verbatim}
instance (Circuit inn WellSized, Width :<: inn, WellSized :<: inn) => 
          Circuit inn WellSized where
  identity (Proxy :: Proxy inn) w = WellSized True
  fan      (Proxy :: Proxy inn) w = WellSized True
  above x y    = WellSized (gwellSized x && gwellSized y 
                            && gwidth x == gwidth y)
  beside x y   = WellSized (gwellSized x && gwellSized y)
  stretch xs x = WellSized (gwellSized x && length xs == gwidth x)
\end{verbatim}

We also need to modify the instance for circuit composition:

 \begin{verbatim}
instance (Circuit inn inn1, Circuit inn inn2) => 
          Circuit inn (Compose inn1 inn2) where
  identity (Proxy :: Proxy inn) w = 
           ((identity (Proxy :: Proxy inn) w) :: inn1,
            (identity (Proxy :: Proxy inn) w) :: inn2)
  fan      (Proxy :: Proxy inn) w = 
           ((fan (Proxy :: Proxy inn) w)      :: inn1,
            (fan (Proxy :: Proxy inn) w)      :: inn2)
  above x y    = ((above x y)    :: inn1, (above x y)    :: inn2)
  beside x y   = ((beside x y)   :: inn1, (beside x y)   :: inn2)
  stretch xs x = ((stretch xs x) :: inn1, (stretch xs x) :: inn2)
 \end{verbatim}

The only problem is that due to the restriction of Haskell's type classes, all of the class type variables must be reachable from the free variables of each method type\cite{2}. Therefore, we need the Proxy here for \textit{identity} and \textit{fan} to allow the use of class type \textit{inn}. Also, explicit type annotations are needed for circuit composition.

\subsection{Records}
Another way is to use records to represent circuits. This approach allows us to define dependent interpretations nicely and alleviate us from the pain of using explicit type annotations everywhere. We define the following data type with record syntax for circuit construction:

\begin{verbatim}
data Circuit inn out = Circuit {
  identity :: Int -> out,
  fan      :: Int -> out,
  above    :: inn -> inn -> out,
  beside   :: inn -> inn -> out,
  stretch  :: [Int] -> inn -> out
}
\end{verbatim}

Each interpretation corresponds to a value of the data type. For example, to see whether a circuit is well-formed or not, we define the value \textit{wsAlg}:

\begin{verbatim}
wsAlg :: (Width :<: inn, WellSized :<: inn) => Circuit inn WellSized
wsAlg = Circuit {
  identity = \w    -> WellSized True,
  fan      = \w    -> WellSized True,
  above    = \x y  -> WellSized (gwellSized x && gwellSized y && 
                                 gwidth x == gwidth y),
  beside   = \x y  -> WellSized (gwellSized x && gwellSized y),
  stretch  = \xs x -> WellSized (gwellSized x && length xs == gwidth x)
}
\end{verbatim}

Circuit composition can also be defined as a value of the data type:

\begin{verbatim}
(<+>) :: (inn1 :<: inn, inn2 :<: inn) => 
         Circuit inn inn1 -> Circuit inn inn2 -> Circuit inn (Compose inn1 inn2)
(<+>) a1 a2 = Circuit {
  identity = \w    -> (identity a1 w, identity a2 w),
  fan      = \w    -> (fan a1 w, fan a2 2),
  above    = \x y  -> (above a1 (inter x) (inter y), above a2 (inter x) (inter y)),
  beside   = \x y  -> (beside a1 (inter x) (inter y), beside a2 (inter x) (inter y)),
  stretch  = \xs x -> (stretch a1 xs (inter x), stretch a2 xs (inter x))
}
\end{verbatim}

Now we can compose multiple interpretations smoothly. For example, we can compose individual interpretations \textit{widthAlg}, \textit{depthAlg} and \textit{wsAlg} together to get a new value  \textit{cAlg} for composed interpretation:

\begin{verbatim}
cAlg :: Circuit (Compose Depth (Compose Width WellSized)) 
                (Compose Depth (Compose Width WellSized))
cAlg = depthAlg <+> (widthAlg <+> wsAlg)
\end{verbatim}

\subsection{F-Algebras}

\section{Extensibility in Both Dimensions}
So far we've only talked about extensibility in one dimension:

\section{Related Work}

\section{Conclusion}

\begin{thebibliography}{99}

\bibitem{1}
Jeremy Gibbons, Nicolas Wu, \textit{Folding Domain-Specific Languages: Deep and Shallow Embeddings}. \hskip 1em plus 0.5em minus 0.4em\relax ICFP' 14, September 1-6, 2014, Gothenburg, Sweden.

\bibitem{2}

\end{thebibliography}

\end{document}

### 2015-03-29 code/Circuit.hs

@@ -1,0 +1,151 @@
+{-# OPTIONS -XTypeSynonymInstances -XFlexibleInstances -XTypeOperators -XMultiParamTypeClasses -XFlexibleContexts -XOverlappingInstances #-}
+
+module Circuit where
+
+class Circuit circuit where
+  identity :: Int -> circuit
+  fan      :: Int -> circuit
+  above    :: circuit -> circuit -> circuit
+  beside   :: circuit -> circuit -> circuit
+  stretch  :: [Int] -> circuit -> circuit
+
+-- Alternative 1
+{-
+data GCircuit inn out = GCircuit {
+  gidentity :: Int -> out, 
+  gfan      :: Int -> out, 
+  gabove    :: inn -> inn -> out, 
+  gbeside   :: inn -> inn -> out, 
+  gstretch  :: [Int] -> inn -> out
+}-}
+
+newtype Width     = Width     {width :: Int}
+newtype Depth     = Depth     {depth :: Int}
+newtype WellSized = WellSized {wellSized :: Bool}
+newtype Layout1   = Layout1   {layout1 :: [[(Int, Int)]]}
+newtype Layout2   = Layout2   {layout2 :: (Int -> Int) -> [[(Int, Int)]]}
+
+type Compose i1 i2 = (i1, i2)
+
+instance Circuit Width where
+  identity w   = Width w
+  fan w        = Width w
+  above x y    = x
+  beside x y   = Width (width x + width y)
+  stretch xs x = Width (sum xs)
+
+instance Circuit Depth where
+  identity w   = Depth 0
+  fan w        = Depth 1
+  above x y    = Depth (depth x + depth y)
+  beside x y   = Depth (depth x `max` depth y)
+  stretch xs x = x
+
+-- Dependent case 1
+instance (Circuit width, Width :<: width) => 
+          Circuit (Compose WellSized width) where
+  identity w   = (WellSized True, identity w)
+  fan w        = (WellSized True, fan w)
+  above x y    = (WellSized (gwellSized x && gwellSized y 
+                             && (gwidth x == gwidth y)),
+                  above (inter x) (inter y))
+  beside x y   = (WellSized (gwellSized x && gwellSized y),
+                  beside (inter x) (inter y))
[…]

### 2015-03-29 code/CircuitInnOut.hs

@@ -8,9 +8,9 @@ data Proxy a = Proxy
 class Circuit inn out where
   identity :: Proxy inn -> Int -> out
   fan      :: Proxy inn -> Int -> out
-  above    :: inn -> inn -> out
-  beside   :: inn -> inn -> out
-  stretch  :: [Int] -> inn -> out
+  above    :: inn       -> inn -> out
+  beside   :: inn       -> inn -> out
+  stretch  :: [Int]     -> inn -> out
 
 newtype Width     = Width     {width :: Int}
 newtype Depth     = Depth     {depth :: Int}
@@ -32,20 +32,24 @@ instance (Circuit inn Depth, Depth :<: inn) => Circuit inn Depth where
   beside x y                      = Depth (gdepth x `max` gdepth y)
   stretch xs x                    = Depth (gdepth x)
 
-instance (Circuit inn WellSized, Width :<: inn, WellSized :<: inn)
-         => Circuit inn WellSized where
+instance (Circuit inn WellSized, Width :<: inn, WellSized :<: inn) => 
+          Circuit inn WellSized where
   identity (Proxy :: Proxy inn) w = WellSized True
   fan      (Proxy :: Proxy inn) w = WellSized True
-  above x y    = WellSized (gwellSized x && gwellSized y && gwidth x == gwidth y)
+  above x y    = WellSized (gwellSized x && gwellSized y 
+                            && gwidth x == gwidth y)
   beside x y   = WellSized (gwellSized x && gwellSized y)
   stretch xs x = WellSized (gwellSized x && length xs == gwidth x)
 
 -- x, y :: inn, no need to use inter here
-instance (Circuit inn inn1, Circuit inn inn2) => Circuit inn (Compose inn1 inn2) where
-  identity (Proxy :: Proxy inn) w = ((identity (Proxy :: Proxy inn) w) :: inn1,
-                                     (identity (Proxy :: Proxy inn) w) :: inn2)
-  fan      (Proxy :: Proxy inn) w = ((fan (Proxy :: Proxy inn) w)      :: inn1,
-                                     (fan (Proxy :: Proxy inn) w)      :: inn2)
+instance (Circuit inn inn1, Circuit inn inn2) => 
+          Circuit inn (Compose inn1 inn2) where
+  identity (Proxy :: Proxy inn) w = 
+           ((identity (Proxy :: Proxy inn) w) :: inn1,
[…]

### 2015-03-29 code/CircuitTF.hs

@@ -1,0 +1,89 @@
+{-# OPTIONS -XTypeSynonymInstances -XFlexibleInstances -XTypeOperators -XMultiParamTypeClasses -XFlexibleContexts -XOverlappingInstances -XIncoherentInstances -XNoMonomorphismRestriction -XDeriveFunctor -XUndecidableInstances -XTypeFamilies #-}
+
+module CircuitTF where
+
+type Compose i1 i2 = (i1, i2) 
+
+class Circuit inn out where
+  type Super inn out :: *
+  identity :: Int -> out
+  fan      :: Int -> out
+  above    :: Super inn out -> Super inn out -> out
+  beside   :: Super inn out -> Super inn out -> out
+  stretch  :: [Int] -> Super inn out -> out
+
+-- id2 :: Circuit inn out => Int -> out
+-- id2 = identity
+
+newtype Width     = Width     {width :: Int}
+newtype WellSized = WellSized {wellSized :: Bool}
+
+instance (Width :<: inn) => Circuit inn Width where
+  type Super inn Width = inn
+  identity w   = Width w
+  fan w        = Width w
+  above x y    = Width (gwidth x)
+  beside x y   = Width (gwidth x + gwidth y)
+  stretch xs x = Width (sum xs)
+
+instance (Width :<: inn, WellSized :<: inn) => Circuit inn WellSized where
+  type Super inn WellSized = inn
+  identity w   = WellSized True
+  fan w        = WellSized True
+  above x y    = WellSized (gwellSized x && gwellSized y && gwidth x == gwidth y)
+  beside x y   = WellSized (gwellSized x && gwellSized y)
+  stretch xs x = WellSized (gwellSized x && length xs == gwidth x)
+
+instance (Circuit inn out1, Circuit inn out2) => Circuit inn (Compose out1 out2) where
+  type Super inn (Compose out1 out2) = inn
+  identity w = undefined
+  fan w = undefined
+  above x y = ((above (inter x) (inter y)) :: out1, 
+               (above (x :: Super inn out2) (y :: Super inn out2)) :: out2)
+  beside x y = undefined
+  stretch xs x = undefined
+
+ 
+class i :<: e where
+  inter :: e -> i
+
+instance i :<: i where
+  inter = id
+
+instance i :<: (Compose i i2) where
+  inter = fst
+ 
+instance (i :<: i2) => i :<: (Compose i1 i2) where
[…]

### 2015-03-29 code/circuitTC.hs

@@ -19,28 +19,6 @@ data GCircuit inn out = GCircuit {
   gstretch  :: [Int] -> inn -> out
 }-}
 
-data Proxy a = Proxy
-
--- Alternative 2
-class GCircuit inn out where 
-  gidentity :: Proxy inn -> Int -> out
-  gfan      :: Proxy inn -> Int -> out
-  gabove    :: inn -> inn -> out 
-  gbeside   :: inn -> inn -> out 
-  gstretch  :: [Int] -> inn -> out
- 
-gid :: GCircuit inn out => Proxy inn -> Int -> out
-gid = gidentity 
-
-gid2 :: GCircuit Width out => Int -> out
-gid2 = gidentity (Proxy :: Proxy Width)
-
-data CircuitF r = Identity Int | Fan Int | Above r r | Beside r r | Stretch [Int] r
-
--- Alternative 3
-class FCircuit inn out where
-   alg :: CircuitF inn -> out
-
 newtype Width     = Width     {width :: Int}
 newtype Depth     = Depth     {depth :: Int}
 newtype WellSized = WellSized {wellSized :: Bool}
@@ -64,24 +42,23 @@ instance Circuit Depth where
   stretch xs x = x
 
 -- Dependent case 1
-instance (Circuit width, Width :<: width) => Circuit (Compose WellSized width) where
+{-instance (Circuit width, Width :<: width) => Circuit (Compose WellSized width) where
   identity w   = (WellSized True, identity w)
-  fan w        = (WellSized True, identity w)
-  above x y    = (WellSized (ws x && ws y && (wd x == wd y))
+  fan w        = (WellSized True, fan w)
+  above x y    = (WellSized (gwellSized x && gwellSized y && (gwidth x == gwidth y))
                   , above (inter x) (inter y))
-  beside x y   = (WellSized (ws x && ws y)
+  beside x y   = (WellSized (gwellSized x && gwellSized y)
                   , beside (inter x) (inter y))
-  stretch xs x = (WellSized (ws x && length xs == wd x)
+  stretch xs x = (WellSized (gwellSized x && length xs == gwidth x)
                   , stretch xs (inter x))
+-}
 
-{-
[…]

### 2015-03-29 paper/Main.tex
Up to F-Algebra

@@
 
-\subsection{F-Algebras}
-
 \section{Extensibility in Both Dimensions}
 So far we've only talked about extensibility in one dimension:
+
+\subsection{F-Algebras}
+We've shown that the type class
+
+\begin{verbatim}
+class i :<: e where
+  inter :: e -> i
+\end{verbatim}
+
+works well with both composable and dependent interpretations for shallow embedding.
+In this section, we will show that it also allows adding and composing interpretations modularly for deep embedding.
+We will still use the CircuitF functor for circuit construction, while incorporating our observation functions (i.e.
+algebras for CircuitF) with the above type class.
+An algebra for CircuitF is defined as:
+
+\begin{verbatim}
+type GAlg r a = CircuitF r -> a
+\end{verbatim}
+
+It consists of type r and a, and a function taking a CircuitF of r-values to an a-value. For example, algebras for \textit{width} and \textit{wellSized} can be defined as follows:
+
+\begin{verbatim}
+widthAlg :: (Width :<: r) => GAlg r Width
+widthAlg (Identity w)   = Width w
+widthAlg (Fan w)        = Width w
+widthAlg (Above x y)    = Width (gwidth x)
+widthAlg (Beside x y)   = Width (gwidth x + gwidth y)
+widthAlg (Stretch xs x) = Width (sum xs)
+
+wsAlg :: (WellSized :<: r, Width :<: r) => GAlg r WellSized
+wsAlg (Identity w)   = WellSized True
+wsAlg (Fan w)        = WellSized True
+wsAlg (Above x y)    = WellSized (gwellSized x && gwellSized y && 
+                                  gwidth x == gwidth y)
+wsAlg (Beside x y)   = WellSized (gwellSized x && gwellSized y)
+wsAlg (Stretch xs x) = WellSized (gwellSized x && length xs == gwidth x)
+\end{verbatim}
+
+For composition, we introduce the operator (\textbf{$<$+$>$}), which takes two algebras as inputs and gives back an algebra that returns a composed type:
+
+\begin{verbatim}
+(<+>) :: (a :<: r, b :<: r) => GAlg r a -> GAlg r b -> GAlg r (Compose a b)
+(<+>) a1 a2 (Identity w)   = (a1 (Identity w), a2 (Identity w))
+(<+>) a1 a2 (Fan w)        = (a1 (Fan w), a2 (Fan w))
+(<+>) a1 a2 (Above x y)    = (a1 (Above (inter x) (inter y)), 
+                              a2 (Above (inter x) (inter y)))
+(<+>) a1 a2 (Beside x y)   = (a1 (Beside (inter x) (inter y)), 
+                              a2 (Beside (inter x) (inter y)))
+(<+>) a1 a2 (Stretch xs x) = (a1 (Stretch xs (inter x)), 
+                              a2 (Stretch xs (inter x)))
+\end{verbatim}
+
+\subsection{Modular Reifiable Matching}
 

### 2015-03-29 paper/Main.tex
Starting on MRM

@@
 \section{Introduction}
+% Basic approach without dependency or composition. F-Algebra for deep embedding.
 
@@
 
-Following is the construction of the Brent-Kung parallel prefix circuit:
+Following is a flexibly typed Brent-Kung parallel prefix circuit:
 
 \begin{verbatim}
-c1 :: Circuit circuit => circuit
-c1 = (fan 2 `beside` fan 2) `above`
+c2 :: Circuit circuit => circuit
+c2 = (fan 2 `beside` fan 2) `above`
      stretch [2,2] (fan 2) `above`
@@
 
-Then we can use the above functions to get  different properties of c1, depending on its type.
-For example, \textit{gwidth (c1 :: Compose Width Depth)} and \textit{gdepth (c1 :: Compose Width Depth)} will give us its width and depth,  respectively.
+Then we can use the above functions to get  different properties of c2, depending on its type.
+For example, \textit{gwidth (c1 :: Compose Width Depth)} and \textit{gdepth (c2 :: Compose Width Depth)} will give us its width and depth,  respectively.
 
@@
 
-For composition, we introduce the operator (\textbf{$<$+$>$}), which takes two algebras as inputs and gives back an algebra that returns a composed type:
+For composition, we introduce the operator (\textbf{$<+>$}), which takes two algebras as inputs and gives back an algebra that returns a composed type:
 
@@
                               a2 (Stretch xs (inter x)))
+\end{verbatim}
+
+An algebra that returns \textit{Compose Width WellSized} is simply:
+\begin{verbatim}
+cAlg2 = widthAlg <+> wsAlg
+\end{verbatim}
+
+Then we can evaluate circuit c1 defined earlier and get its width by:
+\begin{verbatim}
+gwidth (fold cAlg2 c1)
+\end{verbatim}
+
+And check whether it is well-formed or not by:
+\begin{verbatim}
+gwellSized (fold cAlg2 c1)
 \end{verbatim}

### 2015-04-01 dAlg/mrm.tex
MRM template for paper sketching

%-----------------------------------------------------------------------------
%
%               Template for sigplanconf LaTeX Class
%
% Name:         sigplanconf-template.tex
%
% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
%               file for SIGPLAN conference proceedings.
%
% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
%               sigplanconf-guide.pdf
%
% Author:       Paul C. Anagnostopoulos
%               Windfall Software
%               978 371-2316
%               paul@windfall.com
%
% Created:      15 February 2005
%
%-----------------------------------------------------------------------------

\documentclass[nocopyrightspace]{sigplanconf}

% The following \documentclass options may be useful:

% preprint      Remove this option only once the paper is in final form.
% 10pt          To set in 10-point type instead of 9-point.
% 11pt          To set in 11-point type instead of 9-point.
% authoryear    To obtain author/year citation style instead of numeric.

\usepackage{xcolor}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{doubleequals}
\usepackage{comment}
\usepackage{url}

%% for comments
\input{Preamble}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}

\def\commentbegin{\quad\{\ }
\def\commentend{\}}

\newcommand\SM[1]{\textcolor{red!70!yellow}{[SM: #1]}}
\newcommand\BO[1]{\textcolor{green!70!black}{[BO: #1]}}
\newcommand\SH[1]{\textcolor{blue!70!gray}{[SH: #1]}}

\newcommand\name{{\bf DSL}\xspace}
\newcommand\delete[1]{}

\begin{document}

\special{papersize=8.5in,11in}
\setlength{\pdfpageheight}{\paperheight}
\setlength{\pdfpagewidth}{\paperwidth}

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

% Uncomment one of the following two, if you are not going for the 
% traditional copyright transfer agreement.

%\exclusivelicense                % ACM gets exclusive license to publish, 
                                  % you retain copyright

%\permissiontopublish             % ACM gets nonexclusive license to publish
                                  % (paid open-access papers, 
                                  % short abstracts)

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

\title{Composable Algebra with Dependencies}
%\subtitle{A List-of-Functors Approach to Two-Level Types}

\authorinfo{Bruno C. d. S. Oliveira}
           {University of Hong Kong}
           {bruno@cs.hku.hk}
\authorinfo{Shin-Cheng Mu}
           {Academia Sinica}
           {scm@iis.sinica.edu.tw}
\authorinfo{Shu-Hung You}
           {National Taiwan University}
           {suhorngcsie@gmail.com}
\maketitle

\begin{abstract}

\end{abstract}

%\category{CR-number}{subcategory}{third-level}

% general terms are not compulsory anymore, 
% you may leave them out
%\terms
%term1, term2

%\keywords
%keyword1, keyword2

\input{sections/Introduction}

\input{sections/Overview}

\input{sections/ComposableAlg}

\input{sections/DependentAlg}

\input{sections/Extensibility}

\section{Other representations of algebra}
\label{sec: other-alg}

\input{sections/TypeClassAlg}

\input{sections/RecordAlg}

\input{sections/RelatedWork}

\input{sections/Conclusion}

\begin{comment}
\appendix
\section{Appendix Title}

This is the text of the appendix, if you need one.

\acks

Acknowledgments, if needed.
\end{comment}

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\bibliography{mrm}

\end{document}

%                       Revision History
%                       -------- -------
%  Date         Person  Ver.    Change
%  ----         ------  ----    ------

%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2015-04-01 paper/Main.tex
Typo
MRM template for paper sketching

@@
 
-To state that the semantic domain type i represents is part of a larger collection of types, we use the following type class
+To state that the semantic domain that type i represents is part of a larger collection of types, we use the following type class
 
@@
 \section{Extensibility in Both Dimensions}
-So far we've only talked about extensibility in one dimension:
+So far we've only talked about extensibility in one dimension: \textit{// to be continuted...}
 

### 2015-04-08 code/CircuitMRM_extend.hs
Use type class to support more flexible algebra composition

@@ -73,11 +73,11 @@ wsAlg (Identity w)   = WellSized True
 wsAlg (Fan w)        = WellSized True
 wsAlg (Beside x y)   = WellSized (gwellSized x && gwellSized y)
 
-(<+>) :: (a :<: r, b :<: r) => GAlgB r a -> GAlgB r b -> GAlgB r (Compose a b)
+{-(<+>) :: (a :<: r, b :<: r) => GAlgB r a -> GAlgB r b -> GAlgB r (Compose a b)
 (<+>) a1 a2 (Identity w)   = (a1 (Identity w), a2 (Identity w))
 (<+>) a1 a2 (Fan w)        = (a1 (Fan w), a2 (Fan w))
 (<+>) a1 a2 (Beside x y)   = (a1 (Beside (inter x) (inter y)), 
-                              a2 (Beside (inter x) (inter y)))
+                              a2 (Beside (inter x) (inter y)))-}
 
 -- F-Algebras for extended datatype
 type GAlgD r a = CircuitFD r -> a
@@ -95,10 +95,28 @@ wsAlgD (Above x y)    =  WellSized (gwellSized x && gwellSized y &&
                                     gwidth x == gwidth y)
 wsAlgD (Stretch xs x) = WellSized (gwellSized x && length xs == gwidth x)
 
+{-
 (<++>) :: (a :<: r, b :<: r) => GAlgD r a -> GAlgD r b -> GAlgD r (Compose a b)
 (<++>) a1 a2 (Above x y)    = (a1 (Above (inter x) (inter y)), 
                                a2 (Above (inter x) (inter y)))
 (<++>) a1 a2 (Stretch xs x) = (a1 (Stretch xs (inter x)), a2 (Stretch xs (inter x)))
+-}
+
+-- Composing algebras
+class Comb f r a b where
+  (<+>) :: (f r -> a) -> (f r -> b) -> (f r -> (Compose a b))
+
+instance (a :<: r, b :<: r) =>  Comb CircuitFB r a b where
+  (<+>) a1 a2 (Identity w)   = (a1 (Identity w), a2 (Identity w))
+  (<+>) a1 a2 (Fan w)        = (a1 (Fan w), a2 (Fan w))
+  (<+>) a1 a2 (Beside x y)   = 
+    (a1 (Beside (inter x) (inter y)), a2 (Beside (inter x) (inter y)))
+
[…]

### 2015-04-17 dAlg/mrm.tex
Up to MRM (extensibility)
Figures and citations

@@
 \usepackage{url}
+\usepackage{graphicx}
+\usepackage[export]{adjustbox}
+\graphicspath{ {images/} }
 
@@
 
+\input{sections/Scans}
+
+\input{sections/FAlg}
+
 \input{sections/Overview}
@@
 \label{sec: other-alg}
+
+Apart from functors and F-Algebras, there are other ways to represent and evaluate
+the DSL of parallel prefix circuits. In this section, we will show two other 
+representations, and how they can be used to allow dependent interpretations.
 
@@
 
-\bibliography{mrm}
+%\bibliography{mrm}
+
+\begin{thebibliography}{}
+\softraggedright
+
+\bibitem{gibbons14}
+  Gibbons, Jeremy and Wu, Nicolas.
+  Folding Domain-Specific Languages: Deep and Shallow Embeddings.
+  2014.
+
+\bibitem{sheard04}
+  Sheard, Tim and Pasalic, Emir.
+  Two-level types and parameterized modules.
+  \textit{Journal of Functional Programming}.
+  14(5):547-587, September 2014.
+
+\bibitem{fokkinga90}
+  Fokkinga, Maarten M.
+  Tupling and mutumorphisms.
+  1990.
+
+\bibitem{oliveira15}
+  Oliveira, B.C.d.S., Mu, Shin-Cheng and You, Shu-Hung
+  Modular Reifiable Matching: A List-of-Functors Approach to Two-Level Types
+  February 2015.
+
+\end{thebibliography}
 

### 2015-04-18 dAlg/mrm.tex
Abstract & Introduction (for FYP report)

@@
 
-\authorinfo{Bruno C. d. S. Oliveira}
-           {University of Hong Kong}
-           {bruno@cs.hku.hk}
-\authorinfo{Shin-Cheng Mu}
-           {Academia Sinica}
-           {scm@iis.sinica.edu.tw}
-\authorinfo{Shu-Hung You}
-           {National Taiwan University}
-           {suhorngcsie@gmail.com}
+\authorinfo{Draft}
+           {}
+           {}
+
 \maketitle
@@
 \begin{abstract}
+
+This paper presents composable algebra with dependencies: a new approach to compose 
+algebras together to allow dependent interpretations with {\em fold}. 
+For a given datatype represented by two-evel-types\cite{sheard04}, if one of its 
+interpretations depends on a second interpretation, we compose the algebra correponding 
+to this interpretation with the algebra corresponding to the second one, and use the 
+composed algebra with {\em fold} to evaluate the expression.
 
@@
 
-Apart from functors and F-Algebras, there are other ways to represent and evaluate
+Apart from {\em two-level-types}, there are other ways to represent and evaluate
 the DSL of parallel prefix circuits. In this section, we will show two other 
@@
 
+\bibitem{sheard04}
+  Sheard, Tim and Pasalic, Emir.
+  Two-level types and parameterized modules.
+  \emph{Journal of Functional Programming}.
+  14(5):547-587, September 2014.
+
 \bibitem{gibbons14}
@@
   Folding Domain-Specific Languages: Deep and Shallow Embeddings.
+  \emph{International Conference on Functional Programming}.
   2014.
-
-\bibitem{sheard04}
-  Sheard, Tim and Pasalic, Emir.
-  Two-level types and parameterized modules.
-  \textit{Journal of Functional Programming}.
-  14(5):547-587, September 2014.
 

### 2015-04-18 dAlg/mrm.tex
Related work & Conclusion (for FYP report)

@@
 \bibitem{oliveira15}
-  Oliveira, B.C.d.S., Mu, Shin-Cheng and You, Shu-Hung
-  Modular Reifiable Matching: A List-of-Functors Approach to Two-Level Types
+  Oliveira, B.C.d.S., Mu, Shin-Cheng and You, Shu-Hung.
+  Modular Reifiable Matching: A List-of-Functors Approach to Two-Level Types.
   February 2015.
+
+\bibitem{bahr15}
+  Bahr, Patrick and Axelsson, Emil.
+  Generalising Tree Traversals to DAGs.
+  \emph{Proceedings of the 2015 Workshop on Partial Evaluation and Program Manipulation},
+  pages 27-38.
+  2015
 

### 2015-04-18 dAlg/mrm.tex
Wrap up

@@
 algebras together to allow dependent interpretations with {\em fold}. 
-For a given datatype represented by two-evel-types\cite{sheard04}, if one of its 
-interpretations depends on a second interpretation, we compose the algebra correponding 
-to this interpretation with the algebra corresponding to the second one, and use the 
-composed algebra with {\em fold} to evaluate the expression.
+For a given datatype represented by two-level-types\cite{sheard04}, if one of its 
+interpretations depends on a second one, we compose the algebra correponding 
+to the first interpretation with the one corresponding to the second, and use the 
+composed algebra with {\em fold} to evaluate the expression. We present our approach 
+on top of the domain specific language for parallel prefix circuits.
 
@@
 Apart from {\em two-level-types}, there are other ways to represent and evaluate
-the DSL of parallel prefix circuits. In this section, we will show two other 
+the DSL for parallel prefix circuits. In this section, we will show two other 
 representations, and how they can be used to allow dependent interpretations.

### 2015-05-02 code/Repmin.hs
Modular repmin

@@ -1,0 +1,25 @@
+module Repmin where
+
+data Tree = Leaf Int | Branch Tree Tree
+
+-- Traditional repMin: two traversals
+minTree :: Tree -> Int
+minTree (Leaf n) = n
+minTree (Branch a b) = minTree a `min` minTree b
+
+repTree :: Int -> Tree -> Tree
+repTree k (Leaf n) = Leaf k
+repTree k (Branch a b) = Branch (repTree k a) (repTree k b)
+
+repMin :: Tree -> Tree
+repMin t = repTree (minTree t) t
+
+-- Circular programming
+repMin' :: (Tree, Int) -> (Int, Tree)
+repMin' (Leaf n, r) = (n, Leaf r)
+repMin' (Branch a b, r) = (min1 `min` min2, Branch newTree1 newTree2)
+  where (min1, newTree1) = repMin' (a, r)
+        (min2, newTree2) = repMin' (b, r)
+
+repMin2 tree = newTree
+  where (min, newTree) = repMin' (tree, min)

### 2015-05-02 code/RepminNew.hs

@@ -1,0 +1,89 @@
+{-# OPTIONS -XDeriveFunctor -XTypeSynonymInstances 
+            -XFlexibleInstances -XTypeOperators -XMultiParamTypeClasses 
+            -XFlexibleContexts -XOverlappingInstances -XIncoherentInstances 
+            -XNoMonomorphismRestriction -XDeriveFunctor #-}
+
+module RepminNew where
+
+data TreeF r = Leaf Int | Branch r r
+  deriving Functor
+
+data Tree = In (TreeF Tree)
+
+newtype Replace = R {replace :: Int -> Tree}
+
+minAlg :: (Int :<: r) => TreeF r -> Int
+minAlg (Leaf n)     = n
+minAlg (Branch x y) = gMin x `min` gMin y  
+
+repTreeAlg :: (Replace :<: r) => TreeF r -> Replace
+repTreeAlg (Leaf n)     = R (\k -> leaf k)
+repTreeAlg (Branch a b) = R (\k -> branch (replace (gRep a) k) (replace (gRep b) k))
+
+prettyAlg :: (String :<: r) => TreeF r -> String
+prettyAlg (Leaf n)     = show n
+prettyAlg (Branch x y) = gPretty x ++ " " ++ gPretty y
+
+-- Type class
+class i :<: e where
+  inter :: e -> i
+
+instance i :<: i where
+  inter = id
+
+instance i :<: (Compose i i2) where
+  inter = fst
+
+instance (i :<: i2) => i :<: (Compose i1 i2) where
+  inter = inter . snd
+
+gMin :: (Int :<: r) => r -> Int
+gMin = inter
+
+gRep :: (Replace :<: r) => r -> Replace
+gRep = inter
+
+gPretty :: (String :<: r) => r -> String
+gPretty = inter
+
+-- Composition operator
+type GAlg r a = TreeF r -> a
+type Compose i1 i2 = (i1, i2)
+
+(<+>) :: (a :<: r, b :<: r) => GAlg r a -> GAlg r b -> GAlg r (Compose a b)
+(<+>) a1 a2 (Leaf n)     = (a1 (Leaf n), a2 (Leaf n))
+(<+>) a1 a2 (Branch x y) = 
+  (a1 (Branch (inter x) (inter y)), a2 (Branch (inter x) (inter y)))
+
+-- Smart constructors
+leaf :: Int -> Tree
+leaf = In . Leaf
+
[…]

### 2015-05-03 dAlg/mrm.tex
Improve composition operator for MRM approach

@@
 
-\title{Composable Algebra with Dependencies}
-%\subtitle{A List-of-Functors Approach to Two-Level Types}
+\title{Modular and Dependent Interpretations for Shallow Embeddings}
+%\title{Composable Algebra with Dependencies}
 
@@
 
+\bibitem{oliveira13}
+  Oliveira, B.C.d.S., Storm, Tijs van der, Loh, Alex and Cook, William R.
+  Feature-Oriented Programming with Object Algebra
+  \emph{ECOOP'13 Proceedings of the 27th European conference on Object-Oriented Programming},
+  pages 27-51.
+  2013
+
 \end{thebibliography}

### 2015-05-04 dAlg/mrm.tex
Thoughts

@@
 
-\title{Modular and Dependent Interpretations for Shallow Embeddings}
-%\title{Composable Algebra with Dependencies}
+\title{Expressive, Modular and Compositional Embedded DSLs}
+\subtitle{(Functional Pearl)}
 
@@
 \begin{abstract}
+Compositionality is a desirable characteristic for the semantics of
+DSLs. In functional programming folds are used to enforce
+compositionality. However folds make certain compositional
+interpretations hard to express modularly. This pearl presents a
+simple technique that allows non-trivial, but compositional
+interpretations of DSLs to be expressed in a fully modular way
+using folds.
+
+\begin{comment}
 
@@
 on top of the domain specific language for parallel prefix circuits.
+
+\end{comment}
 

### 2015-05-07 code/Context.hs
Layout with records

@@ -1,0 +1,118 @@
+{-# OPTIONS -XTypeSynonymInstances -XFlexibleInstances -XTypeOperators -XMultiParamTypeClasses -XFlexibleContexts -XOverlappingInstances -XIncoherentInstances -XNoMonomorphismRestriction -XDeriveFunctor #-}
+
+module Context where
+
+data Circuit inn out = Circuit {
+  identity :: Int -> out,
+  fan      :: Int -> out,
+  above    :: inn -> inn -> out,
+  beside   :: inn -> inn -> out,
+  stretch  :: [Int] -> inn -> out
+}
+
+newtype Width     = Width     {width :: Int}
+newtype Depth     = Depth     {depth :: Int}
+newtype WellSized = WellSized {wellSized :: Bool}
+newtype Layout    = Layout    {layout :: (Int -> Int) -> [[(Int, Int)]]}
+
+type Compose i1 i2 = (i1, i2)
+
+widthAlg :: (Width :<: inn) => Circuit inn Width 
+widthAlg = Circuit {
+  identity = \w    -> Width w,
+  fan      = \w    -> Width w,
+  above    = \x y  -> Width (gwidth x),
+  beside   = \x y  -> Width (gwidth x + gwidth y),
+  stretch  = \xs x -> Width (sum xs)
+}
+
+depthAlg :: (Depth :<: inn) => Circuit inn Depth 
+depthAlg = Circuit {
+  identity = \w    -> Depth 0,
+  fan      = \w    -> Depth 1,
+  above    = \x y  -> Depth (gdepth x + gdepth y),
+  beside   = \x y  -> Depth (gdepth x `max` gdepth y),
+  stretch  = \xs x -> Depth (gdepth x)
+}
+
+wsAlg :: (Width :<: inn, WellSized :<: inn) => Circuit inn WellSized
+wsAlg = Circuit {
+  identity = \w    -> WellSized True,
+  fan      = \w    -> WellSized True,
+  above    = \x y  -> WellSized (gwellSized x && gwellSized y && 
+                                 gwidth x == gwidth y),
+  beside   = \x y  -> WellSized (gwellSized x && gwellSized y),
+  stretch  = \xs x -> WellSized (gwellSized x && length xs == gwidth x)
+}
+
+layoutAlg :: (Width :<: inn, Layout :<: inn) => Circuit inn Layout
[…]

### 2015-05-07 code/Context.hs
Layout with F-Algebra

@@ -56,6 +56,11 @@ layoutAlg = Circuit {
     Layout (\f -> glayout x (pred . ((scanl1 (+) xs)!!) . f))
 }
 
+lzw :: (a -> a -> a) -> [a] -> [a] -> [a]
+lzw f [] ys         = ys
+lzw f xs []         = xs
+lzw f (x:xs) (y:ys) = f x y : lzw f xs ys
+
 (<+>) :: (inn1 :<: inn, inn2 :<: inn) => 
          Circuit inn inn1 -> Circuit inn inn2 -> Circuit inn (Compose inn1 inn2)
 (<+>) a1 a2 = Circuit {
@@ -65,11 +70,6 @@ layoutAlg = Circuit {
   beside   = \x y  -> (beside a1 (inter x) (inter y), beside a2 (inter x) (inter y)),
   stretch  = \xs x -> (stretch a1 xs (inter x), stretch a2 xs (inter x))
 }
-
-lzw :: (a -> a -> a) -> [a] -> [a] -> [a]
-lzw f [] ys         = ys
-lzw f xs []         = xs
-lzw f (x:xs) (y:ys) = f x y : lzw f xs ys
 
 class i :<: e where
   inter :: e -> i

### 2015-05-20 code/ContextFAlg.hs
Format & small changes

@@ -1,0 +1,125 @@
+{-# OPTIONS -XTypeSynonymInstances -XFlexibleInstances -XTypeOperators -XMultiParamTypeClasses -XFlexibleContexts -XOverlappingInstances -XIncoherentInstances -XNoMonomorphismRestriction -XDeriveFunctor #-}
+
+module CircuitF where
+
+-- Deep embedding?
+data CircuitF r = 
+    Identity Int
+  | Fan Int
+  | Above r r 
+  | Beside r r
+  | Stretch [Int] r
+  deriving Functor
+
+newtype Width     = Width     {width :: Int}
+newtype Depth     = Depth     {depth :: Int}
+newtype WellSized = WellSized {wellSized :: Bool}
+newtype Layout    = Layout    {layout :: (Int -> Int) -> [[(Int, Int)]]}
+
+-- F-Algebra
+widthAlg :: (Width :<: r) => CircuitF r -> Width
+widthAlg (Identity w)   = Width w
+widthAlg (Fan w)        = Width w
+widthAlg (Above x y)    = Width (gwidth x)
+widthAlg (Beside x y)   = Width (gwidth x + gwidth y)
+widthAlg (Stretch xs x) = Width (sum xs)
+
+depthAlg :: (Depth :<: r) => CircuitF r -> Depth
+depthAlg (Identity w)   = Depth 0
+depthAlg (Fan w)        = Depth 1
+depthAlg (Above x y)    = Depth (gdepth x + gdepth y)
+depthAlg (Beside x y)   = Depth (gdepth x `max` gdepth y)
+depthAlg (Stretch xs x) = Depth (gdepth x)
+
+wsAlg :: (WellSized :<: r, Width :<: r) => CircuitF r -> WellSized
+wsAlg (Identity w)   = WellSized True
+wsAlg (Fan w)        = WellSized True
+wsAlg (Above x y)    = WellSized (gwellSized x && gwellSized y && 
+                                  gwidth x == gwidth y)
+wsAlg (Beside x y)   = WellSized (gwellSized x && gwellSized y)
+wsAlg (Stretch xs x) = WellSized (gwellSized x && length xs == gwidth x)
+
+layoutAlg :: (Width :<: r, Layout :<: r) => CircuitF r -> Layout
+layoutAlg (Identity w)   = Layout (\f -> [])
[…]

### 2015-05-20 dAlg/mrm.tex
Introduction
Revised Section 2
Format & small changes
JFP format

@@
 
-\documentclass[nocopyrightspace]{sigplanconf}
+\documentclass{jfp1}
 
@@
 \usepackage{xspace}
-\usepackage{amsmath}
-\usepackage{amsthm}
+%\usepackage{amsmath}
+%\usepackage{amsthm}
 \usepackage{doubleequals}
@@
 \newcommand\SM[1]{\textcolor{red!70!yellow}{[SM: #1]}}
-\newcommand\BO[1]{\textcolor{green!70!black}{[BO: #1]}}
+\newcommand\bruno[1]{\textcolor{green!70!black}{[BO: #1]}}
 \newcommand\SH[1]{\textcolor{blue!70!gray}{[SH: #1]}}
@@
 
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
+%\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
+%\copyrightyear{20yy} 
+%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
+%\doi{nnnnnnn.nnnnnnn}
 
@@
 
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
+%\titlebanner{banner above paper title}        % These are ignored unless
+%\preprintfooter{short description of paper}   % 'preprint' option specified.
 
@@
 
-\authorinfo{Draft}
-           {}
-           {}
+\author[P. Boya and B. C. d. S. Oliveira]
+        {PENG BOYA and BRUNO C. d. S. OLIVEIRA\\
+         The University of Hong Kong, Hong Kong\\
+         \email{bruno@cs.hku.hk}}\bruno{Fix author info later!}
+
+%\authorinfo{Draft}
+%           {}
+%           {}
 
@@
 Compositionality is a desirable characteristic for the semantics of
-DSLs. In functional programming folds are used to enforce
+DSLs. In functional programming folds can be used to enforce
 compositionality. However folds make certain compositional
@@
 \begin{thebibliography}{}
-\softraggedright
+%\softraggedright
 

### 2015-05-22 dAlg/mrm.tex
Refactoring early parts of the paper
Small changes
Section 4.1, 4.2
Section 4.3, 4.4 (multiple & dependent interpretation)
Context sensitive interpretation (part)
Clean up for type-class and record

@@
 
+\newcommand\emma[1]{\textcolor{magenta}{[EM: #1]}}
+
 \newcommand\name{{\bf DSL}\xspace}
@@
 
-\title{Expressive, Modular and Compositional Embedded DSLs}
+\title{Compositionality and Modularity Together at Last!}
 \subtitle{(Functional Pearl)}
 
-\author[P. Boya and B. C. d. S. Oliveira]
-        {PENG BOYA and BRUNO C. d. S. OLIVEIRA\\
+\author[B. Peng and B. C. d. S. Oliveira]
+        {BOYA PENG and BRUNO C. d. S. OLIVEIRA\\
          The University of Hong Kong, Hong Kong\\
-         \email{bruno@cs.hku.hk}}\bruno{Fix author info later!}
+         \email{bruno@cs.hku.hk}}
 
@@
 using folds.
-
-\begin{comment}
-
-This paper presents composable algebra with dependencies: a new approach to compose 
-algebras together to allow dependent interpretations with {\em fold}. 
-For a given datatype represented by two-level-types\cite{sheard04}, if one of its 
-interpretations depends on a second one, we compose the algebra correponding 
-to the first interpretation with the one corresponding to the second, and use the 
-composed algebra with {\em fold} to evaluate the expression. We present our approach 
-on top of the domain specific language for parallel prefix circuits.
-
-\end{comment}
-
 \end{abstract}
@@
 
+\input{sections/Technique}
+
 \input{sections/Scans}
@@
 
-\input{sections/Overview}
+%\input{sections/Overview}
 
-\input{sections/ComposableAlg}
+\input{sections/MultipleAlg}
 
@@
 
-\input{sections/Extensibility}
+\input{sections/Context}
 
-\section{Other representations of algebra}
-\label{sec: other-alg}
-
-Apart from {\em two-level-types}, there are other ways to represent and evaluate
-the DSL for parallel prefix circuits. In this section, we will show two other 
-representations, and how they can be used to allow dependent interpretations.
+%\input{sections/Extensibility}
 
@@
 
-\input{sections/RelatedWork}
+%\input{sections/RelatedWork}
 
@@
 
+\bibitem{blelloch90}  
+  Blelloch, Guy E..
+  Prefix sums and their applications
+  \emph{Technical Report}
+  1990
+
 \bibitem{fokkinga90}

### 2015-07-08 dAlg/mrm.tex
More text (up to Context)
Code for data type a la carte
Finishing up data type a la carte
Text for Grammars

@@
 \graphicspath{ {images/} }
+\usepackage{dirtytalk}
 
@@
 
-%\input{sections/Extensibility}
+\input{sections/DTC}
 
@@
 
-\input{sections/RecordAlg}
+%\input{sections/RecordAlg}
+
+\input{sections/Grammar}
 
@@
 
+\bibitem{gibbons98}
+  Gibbons, Jeremy and Jones, Geraint.
+  The under-appreciated unfold.
+  \emph{International Conference on Functional Programming},
+  pages 273-279.
+  Baltimore, Maryland, September 1998
+
+\bibitem{swierstra08}
+  Swierstra, Wouter.
+  Datatypes \`a la Carte.
+  \emph{Journal of Functional Programming},
+  18(4):423-436,
+  2008
+
+\bibitem{oliveira12}
+  Olivera, B.C.d.S, and Cook, William R.
+  Functional Programming with Structured Graphs.
+  \emph{ICFP '12 Proceedings of the 17th ACM SIGPLAN international conference on Functional programming},
+  Pages 77-88,
+  2012
+
+\bibitem{chlipala08}
+  Chlipala, A.
+  Parametric higher-order abstract syntax for mechanized semantics.
+  \emph{ICFP’08}, 
+  2008.
+
 \end{thebibliography}
